Initial Analysis

### 2019-11-07 Initial_Analysis.Rmd
Included the janitor package and some details on the Species Status function

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "data.table", # Read dataframe (Fast!)
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "wesanderson",
  "tidyverse",
  "circlize", # For circular plot
  "ggimage", #for reading images to the circular plot
  # "cowplot",
  # "rgdal",
  # "RColorBrewer",
  # "knitr",
  # "kableExtra",
  "ggrepel", # for nice plot labels
  "ggsflabel", # for nice sf_plots labels
  # "gridExtra",
  # "ggmap",
  # "rgeos",
  # "stringr",
  # "stringer",
  "spdep", # for poly2nb
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  "purrr",#Spatial analysis
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  # "png", # For reading plots in chunk codes
  # "grid" # For reading plots in chunk codes
  "parallel", # for parallelization
  "taxize", # For getting species names
  "rfishbase", # for species ecosystem affinity
  "zoo" #for runing mean
)

@@

@@

Spp <- 600006
Coord <- CoorG

@@

  # Fix cases where you have equal categories.
  Duplicates <- Determine_Status_Data %>% 
    ungroup() %>% 
    janitor::get_dupes(Territory) %>% 
    select(TaxonKey,Territory) %>% 
    pull(Territory) %>% 
    unique()

@@

```{r Spp_Status_Sub_Routine, eval = T, echo = F}
# Needs to have trans species 
Species_Status <- bind_rows(
    mclapply(
      Species_List,
      FUN = EstSppStatus,
      Coord = CoorG  # Gabriels coordinate system for read species dist
    )
  )

>>>>

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "data.table", # Read dataframe (Fast!)
  "wesanderson",
  "tidyverse", # for all data wrangling and ggplot
  "janitor", # for data cleaning
  "circlize", # For circular plot
  "ggimage", #for reading images to the circular plot
  # "cowplot",
  # "rgdal",
  # "RColorBrewer",
  # "knitr",
  # "kableExtra",
  "ggrepel", # for nice plot labels
  "ggsflabel", # for nice sf_plots labels
  # "gridExtra",
  # "ggmap",
  # "rgeos",
  # "stringr",
  # "stringer",
  "spdep", # for poly2nb
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  "purrr",#Spatial analysis
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  # "png", # For reading plots in chunk codes
  # "grid" # For reading plots in chunk codes
  "parallel", # for parallelization
  "taxize", # For getting species names
  "rfishbase", # for species ecosystem affinity
  "zoo" #for runing mean
)

@@

Finally we choose the reporting year based on the most frequent status in the last 10 years of data. In cases where there was a mach between status (e.g. Cayman Islands for species 6000006 had 5 *Max Exploited* and 5 *Overexploted*) then we report the status at the last year of data.

@@

Spp <- 600004

@@

  # Fix cases where you have equal categories.
  suppressMessages( # supresses "No duplicate combinations found of: Territ"
    Duplicates <- Determine_Status_Data %>% 
      ungroup() %>% 
      janitor::get_dupes(Territory) %>% 
      select(TaxonKey,Territory) %>% 
      pull(Territory) %>% 
      unique()
  )

@@

```{r Spp_Status_Sub_Routine, eval = T, echo = F}
# Needs to have trans species 
Species_Status <- bind_rows(
    mclapply(
      Species_List[1:2],
      FUN = EstSppStatus,
      Coord = CoorG  # Gabriels coordinate system for read species dist
    )
  )
